Embracing the Laws of Physics: \\ Reversible Models of Computation

### 2017-12-22 survey/survey.tex
use the same capitalization for the same ref.

Traditional models of computation are all unityped, generally
operating on unstructured sequences of symbols. But recent
investigations, in the intersection between mathematics and
computer science (particularly in Homotopy Type Theory~\cite{HoTT-book})
reveal that not only can mathematics be typed, but that doing so
reveals further structure -- in both mathematics and in computation.

>>>>

Traditional models of computation are all unityped, generally
operating on unstructured sequences of symbols. But recent
investigations, in the intersection between mathematics and
computer science (particularly in Homotopy Type Theory~\cite{hott-book})
reveal that not only can mathematics be typed, but that doing so
reveals further structure -- in both mathematics and in computation.
